---
title: "Project"
author: "Marwah Talbeh"
date: "2022-11-15"
output: pdf_document
---

```{r}
library(tidyverse)
```

```{r}
data <- read.csv("readmission.csv", header = TRUE, sep = ",")
dim(data)
```

```{r}
colnames(data)
```

```{r}
new_data <- subset(data, select = -c(6))
```

```{r}
colnames(new_data)
```
## we are trying to remove all the null values in our data
```{r}
new_data$Number.of.Discharges<-replace(new_data$Number.of.Discharges,new_data$Number.of.Discharges=="N/A","NA")

new_data$Predicted.Readmission.Rate<-replace(new_data$Predicted.Readmission.Rate,new_data$Predicted.Readmission.Rate=="N/A","NA")

new_data$Expected.Readmission.Rate<-replace(new_data$Expected.Readmission.Rate,new_data$Expected.Readmission.Rate=="N/A","NA")

new_data$Number.of.Readmissions<-replace(new_data$Number.of.Readmissions,new_data$Number.of.Readmissions=="N/A","NA")

```


```{r}
data1 <- subset(new_data, Number.of.Discharges != "NA")
data2 <- subset(data1, Predicted.Readmission.Rate != "NA")
data3 <- subset(data2, Expected.Readmission.Rate != "NA")
data4 <- subset(data3, Number.of.Readmissions != "NA")
data5 <-  subset(data4, Number.of.Readmissions != "Too Few to Report")
dim(data5)
data5
```
 
## Now we will change the medical condition names into a numerical value, so that it would be easier to use when performing our analysis.
```{r}
data5$Measure.Name<-replace(data5$Measure.Name,data5$Measure.Name=="READM-30-HIP-KNEE-HRRP","128")


data5$Measure.Name<-replace(data5$Measure.Name,data5$Measure.Name=="READM-30-CABG-HRRP","111")

data5$Measure.Name<-replace(data5$Measure.Name,data5$Measure.Name=="READM-30-AMI-HRRP","167")

data5$Measure.Name<-replace(data5$Measure.Name,data5$Measure.Name=="READM-30-HF-HRRP","342")

data5$Measure.Name<-replace(data5$Measure.Name,data5$Measure.Name=="READM-30-COPD-HRRP","228")

data5$Measure.Name<-replace(data5$Measure.Name,data5$Measure.Name=="READM-30-PN-HRRP","059")

data5

```

## group the conditions by state

```{r}
data4$Number.of.Readmissions = as.numeric(data4$Number.of.Readmissions)
is.numeric(data4$Number.of.Readmissions)
data4

```

```{r}
library(dplyr)

data4 %>%
  group_by(State, Measure.Name) %>%
  summarise(Readmission_sum=sum(Number.of.Readmissions))
```



## statistical analysis


```{r}

data4$Measure.Name = as.factor(data4$Measure.Name)
is.factor(data4$Measure.Name)
data4


boxplot( Number.of.Readmissions~ Measure.Name, data= data4,
        main=" Boxplot of condition vs number of readmission",
        xlab= "condition", ylab="number of readmission", col=rainbow(6),ylim=c(0,300))
```


```{r}
kruskal.test(Number.of.Readmissions ~ Measure.Name, data= data4)
```

```{r}
tapply(data4$Number.of.Readmissions, data4$Measure.Name, median, na.rm=TRUE)
```

Ho: Median(AMI) = Median(CABG) = Median(COPD) = Median(HF) = Median(HIP) = Median(PN)

Ha: At least one group median differs

Test statistic: chi-squared = 2094.2

P-value: 2.2 * 10^-16

Conclusion(at the 0.05 alpha level): Reject Ho in favor of Ha. There is sufficient evidence to conclude that at least one group median differs.
 
```{r}
pairwise.wilcox.test(data4$Number.of.Readmissions, data4$Measure.Name, p.adjust.method="bonferroni")
```

It looks like there is significant difference across all groups.




